A new tidy data structure to support exploration and modeling of temporal data

### 2019-11-12 cover-letter/cover-letter.Rmd
editted cover letter

We have addressed minor issues that the referees have pointed out on our manuscript titled, "A new tidy data structure to support exploration and modeling of temporal data,".

Two zip files are attached with this submission:

>>>>

We have addressed minor issues that the referees have pointed out on our manuscript titled, "A new tidy data structure to support exploration and modeling of temporal data".

The `source` zip file is attached with this submission, to compile the `.pdf` of the manuscript. This zip file contains:

1. `figure/` Figures generated by R for case studies.
2. `img/` Images generated by Sketch to demonstrate conceptual models.
3. `references.bib` Bibliography items used for BibTeX.
4. `tsibble.tex` LaTeX source file.
5. `tsibble.pdf` A duplicate copy of the non-blinded pdf manuscript file.

The supplemental materials contain the R code used for the case studies, available as the `scripts` zip. We mentioned in the "Acknowledgments" section that all materials contained in the paper can be found at <https://github.com/earowang/paper-tsibble>.
